CO Interlopers Eloping from [C~\textsc{ii}] Surveys

### 2019-03-26 paper/ms.tex
Update ms.tex
Remove Fisher matrix section
Add noise limited regime

\section{Multi-field Approach}\label{sec:theory}
We describe the multi-field approach in full generality and state some
results. First, we assume a measurement of each of $\xps{i}{j}$. The relevant
variance and covariances are \citep[e.g.][]{2015JCAP...03..034V}
\beq
\begin{split}
\Var{\xps{i}{j}} &= \xps{i}{j}^2 + \pstot{i}\pstot{j} \\
\Cov{\xps{i}{j}}{\xps{i}{k}} &= \pstot{i}\xps{j}{k} +
\xps{i}{j}\xps{i}{k}\text{.}
\end{split}
\eeq
We are then making a measurement of each of $\xps{i}{j}$, $\xps{j}{k}$,
and $\xps{k}{i}$. We model each of these power spectra as
\beq
\xps{i}{j}(k) = B_i(k) B_j(k) \denps(k)\text{.}
\eeq
That is, we are only working in the regime where $r_{i,j}=1$. What this
translates to is that we may only perform this interloper removal on
sufficiently large scales, i.e. where $k<k_{\text{max}}$, where
$k_{\text{max}}$ is set by wherever the lines $i$ and $j$ start to
decorrelate. The value of $k_{\text{max}}$ is the only aspect of our analysis
that is model dependent. Only considering modes up to a $k_{\text{max}}$ is
analogous to a similar procedure in galaxy surveys where only large-scale
information up to a $k_{\text{max}}$ where linear theory is applicable is used.

>>>>

\section{Multi-field Approach}\label{sec:theory}
We describe the multi-field approach in full generality and state some
results. First, we assume a measurement of each of $\xps{i}{j}$. The relevant
variance and covariances are \citep[e.g.][]{2015JCAP...03..034V}
\beq\label{eq:var_cov}
\begin{split}
\Var{\xps{i}{j}} &= \xps{i}{j}^2 + \pstot{i}\pstot{j} \\
\Cov{\xps{i}{j}}{\xps{i}{k}} &= \pstot{i}\xps{j}{k} +
\xps{i}{j}\xps{i}{k}\text{.}
\end{split}
\eeq
We are then making a measurement of each of $\xps{i}{j}$, $\xps{j}{k}$,
and $\xps{k}{i}$. We model each of these power spectra as
\beq
\xps{i}{j}(k) = B_i(k) B_j(k) \denps(k)\text{.}
\eeq
That is, we are only working in the regime where $r_{i,j}=1$. What this
translates to is that we may only perform this interloper removal on
sufficiently large scales, i.e. where $k<k_{\text{max}}$, where
$k_{\text{max}}$ is set by wherever the lines $i$ and $j$ start to
decorrelate. The value of $k_{\text{max}}$ is the only aspect of our analysis
that is model dependent. Only considering modes up to a $k_{\text{max}}$ is
analogous to a similar procedure in galaxy surveys where only large-scale
information up to a $k_{\text{max}}$ where linear theory is applicable is used.

The Fisher matrix for our measurement is
\beq\label{eq:fisher}
F_{i,j} = 
\int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
\sum_{\substack{l,l'\\l > l'}} \sum_{\substack{m,m'\\m > m'}}
\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
\frac{1}{\Cov{\hat{P}_{l,l'}(k)}{\hat{P}_{m,m'}(k)}} 
\frac{\partial \hat{P}_{m,m'}(k)}{\partial B_j}\text{,}
\eeq
where $l$, $l'$, $m$, and $m'$ sum over all lines being considered. Note that
we can make the substitution
\begin{equation*}
\sum_{\substack{l,l'\\l > l'}} \rightarrow 
\frac{1}{2} \sum_{\substack{l,l'\\l \neq l'}}\text{,}
\end{equation*}
without changing the value of the Fisher matrix. Thus it will sometimes be
easier to compute
\beq\label{eq:fisher4}
F_{i,j} = 
\frac{1}{4} \int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
\sum_{\substack{l,l'\\l \neq l'}} \sum_{\substack{m,m'\\m \neq m'}}
\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
\frac{1}{\Cov{\hat{P}_{l,l'}(k)}{\hat{P}_{m,m'}(k)}} 
\frac{\partial \hat{P}_{m,m'}(k)}{\partial B_j}\text{,}
\eeq

\subsection{Noise-limited Regime} \label{ssec:noise_limited}
We consider the noise-limited regime. In this case, we assume that $N_i \gg
P_i$, so that Equation~\ref{eq:var_cov} reduces to
\beq \label{eq:var_cov_noise}
\begin{split}
\Var{\xps{i}{j}} &= N_iN_j \\
\Cov{\xps{i}{j}}{\xps{i}{k}} &= 0 \text{.}
\end{split}
\eeq
We will also assume a white noise spectrum, so that each $N_i$ is a constant
value. In this case, the computation of the Fisher matrix is quite simple. In
fact, we can rewrite it as
\beq\label{eq:fisher_noisedom}
F_{i,j} = 
\int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
\sum_{\substack{l,l'\\l > l'}}
\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
\frac{1}{\Var{\hat{P}_{l,l'}(k)}}
\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_j}\text{.}
\eeq
For a diagonal element, we can see that we will only get terms when $l=i$ or $l'=i$. Therefore
\beq\label{eq:fisher_noisedom2}
F_{i,i} = 
\int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
\sum_{\substack{l\neq i}}
\frac{B_l^2}{N_iN_l}\denps(k)^2\text{.}
\eeq
Since we are assuming a white noise power spectrum, if we define
\begin{equation*}
V_k = \int \frac{\text{d}k\,k^2}{2\pi^2} \denps(k)^2 V_{\text{surv}}\text{,}
\end{equation*}
then we can simplify Equation~\ref{eq:fisher_noisedom2} to
\beq\label{eq:fisher_noisedom_diag}
F_{i,i} = 
V_k
\sum_{\substack{l\neq i}}
\frac{B_l^2}{N_iN_l}\text{.}
\eeq
For the off-diagonal case, we can see that the only term that will contribute
is when $l=i$ and $l'=j$, or vice-versa. Therefore, we have that
\beq\label{eq:fisher_noisedom_offdiag}
F_{i,j} = V_k
\frac{B_iB_j}{N_iN_j}\text{.}
\eeq
Note that as the number of fields increases, the diagonal elements become much
larger than the off-diagonal elements, assuming the magnitudes of all the
$B_i$'s and $N_i$'s are roughly similar. Therefore, the Fisher matrix becomes
approximately diagonal, as does the covariance matrix, and the errors on the
$B_i$'s become uncorrelated. This matches our naive expectation that
considering additional fields should reduce the degeneracies between each
$B_i$.

\Gus{Inverting}

In the case of three fields labeled $1$, $2$, and $3$, we can explicitly write
down the Fisher matrix as
\beq
F = V_k
\begin{pmatrix}
\frac{B_2^2}{N_1N_2}+\frac{B_3^2}{N_1N_3} & \frac{B_1B_2}{N_1N_2} & \frac{B_1B_3}{N_1N_3} \\
\frac{B_2B_1}{N_2N_1} & \frac{B_3^2}{N_2N_3}+\frac{B_1^2}{N_2N_1} & \frac{B_2B_3}{N_2N_3} \\
\frac{B_3B_1}{N_3N_1} & \frac{B_3B_2}{N_3N_2} & \frac{B_1^2}{N_3N_1}+\frac{B_2^2}{N_3N_2}\text{.}
\end{pmatrix}
\eeq
